Fluid-mechanical erosion creates anisotropic porous media

### 2022-06-11 docs/PhysicsPaper/StokesErosion.tex
continuing on Sec 3

The accuracy of the method is determined by the accuracy of the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
the Stokes double-layer potential as a collection of Cauchy integrals
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
\end{align}
The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense.
Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}

We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use similar
notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the
boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan
curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{align}
  u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
           \Re(v_3'(x)) + \Re(v_4(x)) \\
  u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
           \Im(v_3'(x)) + \Re(v_5(x)),
\end{align}
respectively.

To apply the aforementioned spectrally accurate quadrature rule, we
require the boundary data of the five Cauchy integrals. For $x_0 \in
\gamma$, the boundary data of each of these Cauchy integrals satisfies
the Sokhotski-Plemelj jump relation
\begin{align}
  \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \bd\Omega,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense. For
the Cauchy integral $v_i$, we let $v_i^-$ denote the boundary data that
satisfies~\eqref{eqn:SP}. Once $v_i^-$ is calculated, $v(x)$ and its
derivatives can be determined by the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy,
  \end{alignat}
\end{subequations}

@@

%Applying the same approach as our previous work~\citep{qua-moo2018}, we
%start with the double-layer potential 
%\begin{align}
%  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
%  \frac{1}{\pi}\int_{\bd\Omega} 
%    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
%    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
%%  \label{eqn:velocityDLP}
%\end{align}
%where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
%$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
%is an unknown density function.  We complete the integral equation
%formulation by adding the $M$ Stokeslets,
%$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
%$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
%$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
%$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
%corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
%smooth geometry $\Omega$, the solution of the incompressible Stokes
%equation with a Dirichlet boundary condition $\ff$ is
%\begin{align}
%  \uu(\xx) = \DDD[\eeta](\xx) + 
%    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
%\end{align}
%where the density function, Stokeslets, and rotlets satisfy
%\begin{subequations}
%\label{eqn:BIE}
%\begin{alignat}{3}
%  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
%    \NN_0[\eeta](\xx) \nonumber \\
%    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
%    \quad &&\qquad\xx \in \bd\Omega, \\
%  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
%    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
%  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
%    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
%    &&\qquad \ell = 1,\ldots,M.
%\end{alignat}
%\end{subequations}
%Here, the null space associated with the flux-free condition of $\ff$ is
%addressed with  $\NN_0$ which is the integral operator with kernel
%$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
%this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
%the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
%$\gamma_\ell$, $\ell=1,\ldots,M$.

>>>>

We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use similar
notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the
boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan
curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{align}
  u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
           \Re(v_3'(x)) + \Re(v_4(x)) \\
  u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
           \Im(v_3'(x)) + \Re(v_5(x)),
\end{align}
respectively. The vorticity can be shown to satisfy
\begin{align}
  \omega(x) = \Im(v_1'(x)) + \Re(v_2'(x)) + 
     \Re(v_5'(x)) + \Im(v_4'(x)).
\end{align}
We note that the vorticity only requires first derivatives of Cauchy
integrals, but the stress tensor involves second derivatives.

The accuracy of the method is determined by the accuracy of the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
the Stokes double-layer potential as a collection of Cauchy integrals
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
\end{align}
The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense.
Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v^{-}(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v^{-}(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}
Note that we require second-order derivatives to compute the shear
stress.

@@
